Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-24 Papers/ms.tex
Fixed mass units: all in terms of critical density. No simple b^2

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are square arcseconds (i.e.
a unit mass would have an Einstein radius of one arcsecond).
Assuming a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc, one unit corresponds to 2.07$\times 10^{11} M_\odot$.
\label{fig:masses2}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{masses2.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures. The units are defined by the critical
density, so that a mass of $\pi$ units would have an Einstein radius of one arcsecond.
Assuming a flat cosmology with
$\Omega_m=0.3$, $\Omega_\Lambda=0.7$, and
$H_0=70$ km/s/Mpc, one unit corresponds to 6.59$\times 10^{10} M_\odot$.
\label{fig:masses2}}
\end{center}
\end{figure}
